A Spiking Independent Accumulator Model for\\Winner-Take-All Computation

### 2017-07-17 doc/poster/poster.tex
Layout fixes.

\tcbuselibrary{raster}

@@

\tcbset{
    boxsep=5mm, titlerule=0mm,
    colback=white, colframe=black, arc=0mm,
    fonttitle=\bfseries,
    coltitle=black, colbacktitle=white,
    halign title=center, halign=flush left
}

@@

        \begin{tcolorbox}[title=Motivation, add to width=-2cm]

@@

        \begin{tcolorbox}[title=Neural Engineering Framework, add to width=5cm]

@@

        \begin{tcolorbox}[title=Benchmarks, add to width=-3cm]

@@

        \begin{tcolorbox}[title=Conclusions, add to width=0cm]

>>>>

\tcbuselibrary{raster}
\tcbuselibrary{skins}

@@

\tcbset{
    skin=enhanced,
    boxsep=5mm, titlerule=0mm, titlerule style={white,line width=0mm},
    colback=white, colframe=black, arc=0mm,
    fonttitle=\bfseries,
    coltitle=black, colbacktitle=white,
    halign title=center, halign=flush left
}

@@

        \begin{tcolorbox}[adjusted title=Motivation, add to width=-2cm]

@@

        \begin{tcolorbox}[adjusted title=Neural Engineering Framework, add to width=5cm]

@@

        \begin{tcolorbox}[adjusted title=Benchmarks, add to width=-3cm]

@@

        \begin{tcolorbox}[adjusted title=Conclusions, add to width=0cm]
